Irt plot extra

### 2022-04-04 manuscript.Rmd
minor update
This version is sent for round 3 feedback

ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day]. Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).

To improve model fit we conducted a post-hoc model modification. Modification indices indicated the possibility of cross-loading of the item 37 and 26 [item 37: I purposely leave
a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it
is light outside], thus discarded.  Also, item 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).  By allowing this pair of items (30 $\&$ 41)  to covary their error variance our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).  Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. As such, we accept this model thus finalizing the long Form of LEBA with 23 items. The items are provided in the **Supplementary File 1**.  Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure. **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.

>>>>

ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200)

@@

Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day]. Item pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and item pair 16-17 stemmed from the preference of using blue filtering or coloured glasses during the daytime. Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).

To improve model fit we conducted a post-hoc model modification. Modification indices indicated the possibility of cross-loading of the item 37 and 26 [item 37: I purposely leave
a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it
is light outside] thus discarded.  Also, item 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).  By allowing this pair of items (30 $\&$ 41)  to covary their error variance our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).  Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. As such, we accept this model thus finalizing the long Form of LEBA with 23 items. The items are provided in the **Supplementary File 1**.  Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure. **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.
